An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
meeting notes

\begin{proposition}\label{prop:SL-minimal}
	If loss $L: \R \to \reals^\Y_+$ has polyhedral risk, $\Sc(L)$ is a minimal representative set for $L$.
\end{proposition}
\begin{proof}\jessiet{I don't like this proof, but meh.}
	First, we have to show that $\Sc(L)$ is a representative set.
	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.

@@

\begin{lemma}
	\label{lem:polyhedral-range-gamma}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}
\begin{proof}
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimal Representative Sets, Non-redundancy, and Tight Embeddings}

% commented out 19 Apr 21
%\raf{Some thoughts on this section:
%  \begin{itemize}
%  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
%  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%    \begin{itemize}
%    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%    \end{itemize}
%  \end{itemize}}
%\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
%There are a few results that are well-explained by this:
%\begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
%\end{itemize}
%This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

@@

%\begin{definition}[Non-redundancy]\label{def:nonredundant}
%	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
%	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
%\end{definition}

%commented out 23 Apr 21
%\begin{proposition}\label{prop:min-rep-implies-trim}
%	Suppose $L$ elicits $\Gamma$.
%	If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
%\end{proposition}
%\begin{proof}
%We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
%For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
%
%\jessie{Implicit lemma about 3 ways to be redundant used here.}
%We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
%If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
%If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
%Therefore, $\Gamma_r \in \trim(\Gamma)$.
%\end{proof}
%
%\begin{proposition}
%	Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
%	$L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
%\end{proposition}
%\begin{proof}
%	$\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
%	By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
%	Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
%	In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
%	
%	$\impliedby$
%	We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
%	In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
%	Therefore, $\R$ is not a minimum representative set.
%\end{proof}

@@

%commented out 06 May 21	
%	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
%	
%	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
%	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
%	
%	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
%	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
%	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
%	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
%	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.

%commented out 03 May 21	
%	Suppose $L(u) \in \trim(L)$.
%	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
%	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
%	
%	Now, suppose $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
%	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
%	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
%	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
\end{proof}

@@

%tight version; commented out May 8, 2021
%$(a \implies b)$
%If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
%We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
%If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
%This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
%Therefore, $\U$ is a finite minimum representative set for $L$.
%
%$(b \implies c)$
%We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
%This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
%If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}
%
%
%$(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
%%If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
%For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
%If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
%
%We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
%As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
\end{proof}

@@

%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another. \jessie{Merge with earlier definitions if we keep this section}
%\begin{definition}\label{def:prop-embed}

@@

%\end{definition}

@@

%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
%However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  
%However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.

@@

%\begin{lemma}\label{lem:embed-defs-equiv}

@@

%\end{lemma}
%\begin{proof}

@@

%	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
%	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
%	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
%	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

@@

%	%To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.

@@

%\end{proof}

When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
%it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.

@@

%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	%\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

>>>>

\begin{proposition}\label{prop:SL-minimal}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof.}
\end{proposition}
\begin{proof}\jessiet{I don't like this proof, but meh.}
	First, we have to show that $\Sc(L)$ is a representative set.
	As facets are closed and the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) over the entire facet (and therefore $\Gamma(p) \cap \Sc(L) \ni u_F$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.

@@

\begin{lemma}
	\label{lem:polyhedral-range-gamma}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix}
\end{lemma}
\begin{proof}
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimum Representative Sets, Non-redundancy, and Tight Embeddings}

% commented out 19 Apr 21
% \raf{Some thoughts on this section:
% \begin{itemize}
% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%   \begin{itemize}
%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%   \end{itemize}
% \end{itemize}}
% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
% There are a few results that are well-explained by this:
% \begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
% \end{itemize}
% This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

@@

% \begin{definition}[Non-redundancy]\label{def:nonredundant}
%   A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
%   A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
% \end{definition}

% commented out 23 Apr 21
% \begin{proposition}\label{prop:min-rep-implies-trim}
%   Suppose $L$ elicits $\Gamma$.
%   If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
% \end{proposition}
% \begin{proof}
%   We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
%   For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
%   
%   \jessie{Implicit lemma about 3 ways to be redundant used here.}
%   We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
%   If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
%   If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
%   Therefore, $\Gamma_r \in \trim(\Gamma)$.
% \end{proof}
% 
% \begin{proposition}
%   Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
%   $L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
% \end{proposition}
% \begin{proof}
%   $\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
%   By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
%   Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
%   In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
%   
%   $\impliedby$
%   We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
%   In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
%   Therefore, $\R$ is not a minimum representative set.
% \end{proof}

@@

  % commented out 06 May 21	
  %	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
  %	
  %	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
  %	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
  %	
  %	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
  %	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
  %	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
  %	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
  %	% Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.

  % commented out 03 May 21	
  %	Suppose $L(u) \in \trim(L)$.
  %	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
  %	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  %	
  %	Now, suppose $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  %	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
  %	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
  %	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
\end{proof}

@@

  % tight version; commented out May 8, 2021
  % $(a \implies b)$
  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
  % Therefore, $\U$ is a finite minimum representative set for $L$.
  % 
  % $(b \implies c)$
  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}
  % 
  % 
  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
  % 
  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
\end{proof}

@@

% While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another. \jessie{Merge with earlier definitions if we keep this section}
% \begin{definition}\label{def:prop-embed}

@@

% \end{definition}

@@

% By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
% However, Definitions~\ref{def:loss-embed} and~\ref{def:prop-embed} are not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e., that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  
% However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.

@@

% \begin{lemma}\label{lem:embed-defs-equiv}

@@

% \end{lemma}
% \begin{proof}

@@

%	% Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
%	% We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
%	% Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
%	% Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

@@

%	% To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.

@@

% \end{proof}

When working with convex surrogates which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $\inprod{p}{L}$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), 
% it is useful to consider a transformation which removes redundant level sets, captured by the \emph{trim} operation.

@@

% \btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
% Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.

@@

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
  \item $\U$ is a finite minimum representative set for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
  Let $L$ elicit $\Gamma$.
